\texttt{nevh}: Numerical Evolution from the Hamiltonian

### 2019-08-12 doc/nevh.tex
Cleaned up a bit, added some documentation.

\title{\texttt{nevh}: Numerical Evolution from the Hamiltonian}
\date{\today}
\author{LJM~Amoreira}
\begin{document}
\maketitle
\section{Introduction}
This package computes the trajectories of mechanical systems given their
hamiltonian function and initial state alone.

@@

\section{Hamilton's Equations in Numerical Form}
Hamilton's Equations can be set in a more compact (and more suitable for
numerical resolution using standard routines or in the current approach) form,
\begin{equation}\label{eq:HEterse}
  \dot \psi=f(t,\psi),
\end{equation}
where $\psi=(\psi_1,\,\psi_2,\,\ldots,\,\psi_{2N_f})=(q_i,\,p_i)$,
$i=1,\ldots N_f$ and
\begin{equation}
  f(t,\psi)=
  \begin{pmatrix}
    \mathbb{0}&\mathbb{1}\\
    -\mathbb{1} &\mathbb{O}
  \end{pmatrix}\nabla_\psi H(t,\psi).
\end{equation}
Here, $\mathbb{0}$ and $\mathbb{1}$ represent the $N_f\times N_f$ zero matrix
and identity matrix, respectively, and
\begin{equation*}
  \nabla_\psi H=\left(
    \pd{H}{\psi_1},\,
    \pd{H}{\psi_2},\,\ldots,\,
    \pd{H}{\psi_{2N_f}}
    \right).
\end{equation*}
This package
\end{document}

>>>>

\title{\texttt{nevh}: Numerical Evolution from the Hamiltonian}
\date{\today}
\author{JML~Amoreira\\
  \texttt{jmlamoreira@gmail.com}
  \and LJM~Amoreira\\
  \texttt{amoreira@ubi.pt}
}
\begin{document}
\maketitle
\section{Introduction}
This package computes the trajectories of mechanical systems given their
hamiltonian function and initial state alone.

@@

\section{Hamilton's Equations in Numerical Form}
Hamilton's Equations can be set in a more compact (and more suitable for
numerical resolution using standard routines or in the current approach) form,
\begin{equation}\label{eq:HEterse}
  \dot \psi=f(t,\psi),
\end{equation}
where $\psi=(\psi_1,\,\psi_2,\,\ldots,\,\psi_{2N_f})=(q_i,\,p_i)$,
$i=1,\ldots N_f$ and
\begin{equation}
  f(t,\psi)=
  \begin{pmatrix}
    \mathbb{0}&\mathbb{1}\\
    -\mathbb{1} &\mathbb{O}
  \end{pmatrix}\nabla_\psi H(t,\psi).
\end{equation}
Here, $\mathbb{0}$ and $\mathbb{1}$ represent the $N_f\times N_f$ zero matrix
and identity matrix, respectively, and
\begin{equation*}
  \nabla_\psi H=\left(
    \pd{H}{\psi_1},\,
    \pd{H}{\psi_2},\,\ldots,\,
    \pd{H}{\psi_{2N_f}}
    \right).
\end{equation*}
This package computes $\nabla_\psi H$ using central finite difference formulas
and solves the motion equations using the plain RK4 method. The user only has to
supply de definition of the hamiltonian and the initial state, no need to
explicitly define the Hamilton's equations for the problem.

Some simple examples are presented in the notebook in the \texttt{test/} folder.
\end{document}
